```{r}
install.packages("party")
library(party)
```
```{r}
install.packages("rpart")
```

```{r}
library(rpart)
```

```{r}
D1 <- read.csv("~/Documents/RStudio/assignment5-Yuwen-Zhang/intelligent_tutor.csv")
```

```{r}
c.tree <- rpart(action ~ hint.y + complete, method="class", data=D1) #Notice the standard R notion for a formula X ~ Y

#Look at the error of this tree
printcp(c.tree)

#Plot the tree
post(c.tree, file = "", title = "Session Completion Action: 1 - Ask teacher, 2 - Start new session, 3 - Give up")

```
```{r}
hist(D1$score)
```
```{r}
D1$advice <- ifelse(D1$score <=0.4, "intervene", ifelse(D1$score > 0.4 & D1$score <=0.8, "monitor", "no action"))
```

```{r}
score_ctree <- rpart(factor(advice) ~ prior_prob_count + prior_percent_correct + hints, D1)
```

```{r}
plot(score_ctree)
post(score_ctree, file = "score_ctree.ps")
```

## Please interpret the tree, which two behaviors do you think the teacher should most closely pay attemtion to?

## Teacher should pay attention to student's prior correct percentage and hints they use.

```{r}
D2 <- read.csv("~/Documents/RStudio/assignment5-Yuwen-Zhang/intelligent_tutor_new.csv")
```

```{r}
D2$prediction <- predict(score_ctree, D2)
```

## Part III
Compare the predicted advice with the actual advice that these studnts recieved. What is the difference between the observed and predicted results?


```{r}
D2$actual <- ifelse(D2$score <=0.4, "intervene", ifelse(D2$score > 0.4 & D2$score <=0.8, "monitor", "no action"))
```

```{r}
table(D2$actual == D2$prediction)
```
# All wrong?

